---
title: "NOSE Pre-Clinical Swab Data"
date: "8/16/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)

loadd(cleaned_data)
loadd(stan_model)

cleaned_data <- cleaned_data %>% filter(count < 100)

```



# Colony Counts by Swab Type
This figure shows the colony counts recorded from each of the plates for each of the swab types. The smaller, somewhat transparent dots are the actual count values. The larger, filled dots show the median colony count number for the corresponding swab type.

```{r}

cleaned_data %>% mutate(swab_type = fct_reorder(swab_type, count, na.rm = T))  %>% ggplot(aes(x = swab_type, y = count, color = swab_type)) + 
  geom_jitter(size = 2, alpha = .2, width = .2) + coord_flip() + stat_summary(fun = median, geom = "point", size = 3.5) + theme_light() + scale_color_d3()



```


# Swab Comparison

## Random Effects Model
To compare the swabs, we fit a Poisson random effects model to the nasal swab data. Expected colony count was modeled as

$$
\begin{align*}
log(E[Count]) &= Swab \: Type + Sample
\end{align*}
$$
where Swab Type is entered as a fixed effect categorical predictor with Swab Type = Copan Floq as the reference level and Sample as a random effect. In effect, we are modeling the expected colony count as a function of swab type while accounting for the fact that we expect some counts to be more similar to others either because they are from the same sample.


```{r}

plot(stan_model, regex_pars = "swab_type", prob = .95, prob_outer = .95, transformations = "exp") + geom_vline(xintercept = 1) + scale_y_discrete(labels = levels(cleaned_data$swab_type)[-1])

```

The figure shows estimated coefficient values as well as 95% credible intervals (CIs) for the performance of the swabs relative to the Copan Floq swab. This model estimates multiplicative changes, so that a coefficient value of 1 for a swab type indicates that the expected number of colony counts for that swab is equal to the expected number of colony counts for the Copan Floq swab, while a coefficient value of 0.5 would indicate that the expected number of colony counts for that swab is equal to half of the expected number of colony counts from the Copan Floq swab.

From the figure, we can see that there is no definitive evidence that any of the other swabs outperforms the Copan Floq swab in terms of collecting more colonies. The Origin swab performs closest to the Copan Floq swab, and may potentially perform better. The other swabs are estimated to collect around half of the number of colonies that the Copan Floq swab collects on average. Exact values for the estimated multiplicative change relative to the Copan Floq swab and the upper and lower ends of the 95% CIs are shown in the following table:

```{r}

swab_coef_summary <- summary(stan_model, regex_pars = "swab_type", probs = c(.5, .025, .975))[, c("50%", "2.5%", "97.5%")]

rownames(swab_coef_summary) <- levels(cleaned_data$swab_type)[-1]
colnames(swab_coef_summary) <- c( "Multiplicative Change", "95% CI Lower", "95% CI Upper")
knitr::kable(round(exp(swab_coef_summary), digits = 2))

```


# Potential for Plate Order Effects


The following figure shows the colony counts for each swab type plotted in a sequential order according to plate number. The solid line in each panel separates the first 20 plates from the last 20 plates.
```{r}

cleaned_data %>% ggplot(aes(x = as.numeric(plate_number), y = count, color = swab_type)) + geom_jitter(size = 2, alpha = .5, width = .2)  + theme_light() + facet_wrap( ~ swab_type) + geom_vline(xintercept = 20) + scale_color_d3() + xlab(label = "Plate Number")


```



